Supplementary Material for `The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere'

### 2024-04-23 manuscript.Rmd
Submited version

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
bibliography: JAE_Review.bib
csl: "environmental-reviews.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

>>>>

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
bibliography: JAE_Review.bib
csl: "environmental-reviews.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---
